Global Climate and Atmosphere Composition of the Ultra-Hot Jupiter WASP-103\lowercase{b} from \HST\ and Spitzer Phase Curve Observations

### 2018-01-17 ms.tex
incorporating comments

\author{Gregory L. Henry}
\affiliation{Center of Excellence in Information Systems, Tennessee State University, Nashville, TN 37209, USA}

@@

\begin{abstract}
	We present thermal phase curve measurements for the hot Jupiter WASP-103b observed with \emph{Hubble}/WFC3 and \emph{Spitzer}/IRAC. The dayside planet-to-star flux is $0.151\pm0.015\%$, $0.446\pm0.38\%$, and $0.569\pm0.014\%$ in bandpasses centered at $1.4$, $3.6$, and $4.5\mu$m, respectively.  The phase curves have large amplitudes and negligible hotspot offsets, indicative of poor heat redistribution to the nightside. We fit the phase variation with a range of climate maps and find they all provide reasonable fits to the data, but have large degeneracies in temperature (up to 1000 K for a given latitude/longitude). The phase-resolved spectra are consistent with blackbodies in the WFC3 bandpass, with effective temperatures ranging from 2000 K on the nightside to 3000 K on the dayside. However, the dayside spectrum has a strong feature in the \Spitzer\ bands, which we attribute to CO emission and a thermal inversion.  The emission feature is not present on the nightside, suggesting changing thermal structure with longitude. We retrieved the atmospheric composition with a 1D thermochemical equilibrium model and found the composition is moderately metal-enriched ($\mathrm{[Fe/H]} =  23^{+29}_{-13}\times$ solar), and the carbon-to-oxygen ratio is below 0.9 at $3\,\sigma$ confidence. In contrast to other hot Jupiters, we do not detect significant water absorption, which we attribute to partial H$_2$O dissociation and additional opacity from H- and TiO/VO.  We compare the phase curves to 3D general circulation models and find that atmospheric drag is required to explain the small hotspot offsets, but that these models overpredict the phase curve amplitude.  We also compare the WASP-103b spectra to brown dwarfs and young directly imaged companions and find they have significantly larger water features, indicating that surface gravity and irradiation environment play an important role in shaping the spectra of hot Jupiters. These results highlight the 3D structure of exoplanet atmospheres and illustrate the importance of phase curve observations for understanding their complex chemistry and physics.
\end{abstract}

@@

Exoplanets are so distant that they are not spatially resolved, so the only way to reveal inhomogeneity in their atmospheres is to measure a phase curve. Phase curve observations consist of continuous monitoring of the planet-to-star flux ratio over a complete orbital revolution of the planet, which exposes different longitudes at each orbital phase.  The first phase curve was observed with \Spitzer\ for the hot Jupiter HD 189733b by \citep{knutson07}, followed by additional \Spitzer\ observations for about a dozen more systems \citep[cataloged in][]{parmentier17}.  The observations revealed large day-night temperature contrasts (in excess of 300 K), and eastward shifted peak brightness due to heat circulation, as predicted by 3D models \citep{showman09}.  These infrared measurements were complemented by optical phase curves from \Kepler\, which show evidence for reflected light from patchy and variable dayside clouds with a range of compositions \citep{demory13, hu15, armstrong16, parmentier16}. A \emph{spectroscopic} phase curve was observed for WASP-43b with \emph{Hubble}/Wide Field Camera 3 (\HST/WFC3) in the near-infrared, which provided the first phase-resolved measurements of an exoplanet's water abundance and thermal structure \citep{stevenson14, stevenson17}.

@@

WASP-103b is an archetype of the class of ultra-hot Jupiters (with orbital periods of about one day and dayside temperatures typically $>2000\,\mathrm{K}$). Observations of the thermal emission spectra of these objects have been puzzling. In the near-infrared, where water is the dominant absorber, some spectra show water absorption features, some show emission features, and some are consistent with blackbody models \citep{madhusudhan11, crossfield12, stevenson14b, haynes15, evans16, beatty17a, beatty17b, sheppard17, arcangeli18, mansfield18}.  A variety of explanations have been proposed for these results, including low metallicity or high carbon-to-oxygen compositions, dayside clouds, and isothermal or inverted temperature profiles caused by TiO/VO absorption in the upper atmosphere. Recently, \cite{arcangeli18} showed that water dissociation on the hot dayside plays an important role in the atmospheres of these ultra-hot planets and may be responsible for some of the blackbody-like near-IR spectra. In this work, we put these results in context by investigating the global thermal structure and composition of the ultra-hot Jupiter WASP-103b.

The structure of the paper is the following: in \S\,\ref{sec:observations} we describe the observations and data reduction. \S\,\ref{sec:fits} details the models fit to the phase curves. \S\,\ref{sec:results} we discuss results, including the phase curve amplitudes and hotspot offsets, the phase-resolved spectra, and estimates of the planet's climate. In \S\,\ref{sec:gcm} and \ref{sec:comparison}, we compare the observations to GCM predictions and spectra from similar temperature stars and directly imaged companions. \S\,\ref{sec:summary} concludes.

@@

\subsection{\Spitzer}
We also obtained \Spitzer/IRAC observations with 3.6 and 4.5 $\mu$m photometric filters (referred to as Channel 1 and Channel 2, respectively). The observations had the following setup. Each phase curve observation consisted of 30 hours of time series photometry, beginning three hours prior to one secondary eclipse and ending three hours after a second eclipse.  We used 12 s exposures to maximize the duty cycle without saturating the detector. The data volume is relatively low for this exposure time, so we read out the full array. To minimize the intrapixel effect (variations in flux caused by imprecise pointing), we did not dither and also used PCRS peak-up\footnote{\url{http://irsa.ipac.caltech.edu/data/SPITZER/docs/irac/pcrs\_obs.shtml}} to improve the pointing accuracy. We began each observations with a 30-minute position settling period, followed by three Astronomical Observation Requests (AORs) of equal duration. At the beginning of each AOR, the telescope was repointed to position the target in the ``sweet spot" of the detector.

@@

The photometric analyses are summarized for each observing season in Table\,\ref{tab:photometry}.  The standard deviation of WASP-103's brightness in each season is given in column~4.  The mean of the three standard deviations is 0.0058~mag, which is very comparable to the mean standard deviation of the six comparison stars (0.0055~mag).  To maximize the possibility of detection WASP-103's rotation, we normalized the photometry such that each observing season has the same mean, thereby removing long-term variability in WASP-103 and/or the comparison stars. We performed a periodogram analysis of the normalized dataset. Figure\,\ref{fig:photometry} shows the frequency spectrum and the phase curve computed with the best frequency, respectively.  We also performed a least-squares fit to the data to determine the best fit sine curve. The best fit period is 6.814 days, which agrees closely with the estimated stellar rotation period of 6.855 days \citep{gillon14}.  The variability amplitude is 0.005~mag. Based on the formalism in \cite{zellem17}, we calculate that this variability will bias the measured eclipse depth by $\lesssim10$\,ppm from epoch to epoch, which is well below the photon-limited precision of our measurements.

@@

\section{Light Curve Fits}
\label{sec:fits}
We fit a two-component model to the light curves. One component models the astrophysical signal (the planet's thermal phase variation and transit), and the other component models the systematic noise introduced by time-dependent changes in instrument performance. For each light curve, we fit the physical and systematic components simultaneously, such that the total observed flux as a function of time is given by $F(t) = F_\mathrm{physical}(t) \times F_\mathrm{sys}(t)$. For the \HST\ data, where we observed two phase curves and two additional eclipses, we constrain the physical parameters to be the same for all visits, but allow some of the systematics parameters to vary (for more details see \S\,\ref{sec:hst_sys}). We fit the WFC3 band-integrated (``white" light curve"), as well as spectroscopic light curves created from 10 wavelength bins uniformly spaced at $0.05\,\mu$m intervals between $1.15$ and $1.65\,\mu$m.

@@

Some segments of the data exhibit stronger systematics than others, so we exclude these data in our final analysis. We drop the first orbit from every visit and the first exposure from every orbit \citep[following common practice; see e.g.][]{kreidberg14a}.  We also discard exposures from the last half of orbit 15 from the phase curve observations, which were taken in staring mode to enable a gyro bias update. Since we observed two phase curves, we have complete orbital phase coverage the planet despite discarding some data.

@@

In addition to calculated the fit rms compared to the photon noise, we also tested for the presence of red noise based on whether the rms decreases as expected when the light curve in binned in time.  If the noise is white (uncorrelated in time), the residuals are expected to decrease by a factor of $\sqrt{N}$, where $N$ is the number of points in a bin. Figure\,\ref{fig:rms} shows the binned residuals compared to expectations for white noise. The \HST/WFC3 and \Spitzer\ Channel 2 light curves agree well with expectations, whereas \Spitzer\ Channel 1 shows higher noise than expected as bin size increases. This test confirms the presence of time-correlated noise in the Channel 1 light curve that can be seen by eye in the residuals in Figure\,\ref{fig:phasecurves}. Both \Spitzer\ channels use the same detector, but Channel 1 data are more susceptible to time-correlated noise because the the point spread function is narrower at shorter wavelengths, making intrapixel sensitivity variations more pronounced.

@@

\section{Results}
\label{sec:results}
The fitted light curves are shown in Figure\,\ref{fig:phasecurves}. This figure shows results from the spherical harmonics model for the thermal phase variation and has instrument systematics removed.  Broadly speaking, the phase curves show large dayside planet-to-star flux values, ranging from $0.151\pm0.015\%$, $0.446\pm0.38\%$, and $0.569\pm0.014\%$ in the WFC3 white light curve, and \Spitzer\ $3.6$, and $4.5\mu$m bandpasses, respectively.  The planet flux changes significantly with orbital phase in all three of the data sets, suggesting a strong gradient from dayside to nightside temperature, and peak brightness occurs near phase 0.5. In this section, we quantitatively characterize the phase curve shape, split the data into phase resolved spectra, evaluate different different temperature maps, and compare with previous observations of the dayside thermal emission spectrum.

@@

\begin{figure*}
\includegraphics[width = 1.0\textwidth]{Figures/hst_model_comparison.pdf}
\caption{\textbf{Left:} Fits to the broadband WFC3 phase curve compared to a GCM. The colored lines correspond to different temperature maps fit to the data, and the dashed gray line is from the $\tau_\mathrm{drag3}$ GCM. We also show the planet-to-star flux corresponding to each map (points), which is model-dependent due to slight degeneracies with the instrument systematic model.  \textbf{Right:} Temperature maps from the best fit models and the GCM at a representative photospheric pressure of 0.01 bar.}
\label{fig:model_comparison}
\end{figure*}

@@

\begin{figure}
\includegraphics[width = 0.5\textwidth]{Figures/dayside_spectrum.pdf}
\caption{Dayside emission spectrum (points) compared to the best fit 1-D model (blue line) with $1\,\sigma$ uncertainty shaded in orange. We also show the best fit blackbody (fit to the WFC3 data only).}
\label{fig:dayside}
\end{figure}

\subsection{Climate}
We fit three different models to characterize the planet's climate: a two-temperature map, the physically-motivated kinematic model of \citep{zhang17}, and a spherical harmonic map. We also fit the thermal phase variation with a sinusoid, which can be inverted to map the climate \citep{cowan08}.  All of the models provide reasonable fits to the data, with $\chi^2_\nu$ near unity, but they yield significantly different temperature maps. Table\,\ref{table:model_comparison} lists the minimum and maximum temperatures for the best fit models to the WFC3 broadband and two Spitzer phase curves. We also list the  information criterion (BIC) and Aikike information criterion (AIC) values for the fits \citep[a $\Delta$BIC value greater than 10 constitutes strong evidence against a given model;][]{kass95}.

@@

We compared the planet's minimum and maximum temperature for the three climate maps by computing the temperatures over a $100\times100$ grid in latitude and longitude. The kinematic model has the hottest dayside temperature and the two-temperature model has the smallest. The differences in peak temperature for the models we consider ranges from $630\,\mathrm{K}$ for \Spitzer\ Channel 1 to $1070\,\mathrm{K}$ for the broadband WFC3 light curve. The minimum nightside temperature is also model-dependent: for the WFC3 data, the two-temperature model predicts a nightside temperature of zero Kelvin, whereas the best fit kinematic model has a nightside temperature of $1980\,\mathrm{K}$.  These differences arise because the kinematic model allows a steep temperature gradient on the dayside, so the substellar point is much hotter than the terminator, whereas the two temperature map imposes a constant dayside temperature.  The spherical harmonics model has an intermediate temperature gradient, and fits the data the best. However, this model may not be physically realistic: on the nightside, it produces higher temperatures at the poles than at the equator, contrary to predictions from GCMs (which we discuss in \S\,\ref{sec:gcm}).

@@

\subsection{Blackbody Fits}
A blackbody is the simplest model for the planet's thermal emission and provide a useful first evaluation of the atmospheric properties. The best fit blackbodies are shown in Figures \ref{fig:spectra} and \ref{fig:dayside}. This model performs well for some orbital phases, with $\chi^2_\nu$ ranging from 0.9 to 1.1 for phases $\phi = 0.1, 0.7$ and $0.8$. At other phases the blackbody model is a poorer fit, particularly to the \Spitzer\ data. For phases $0.2 - 0.6$, the \Spitzer\ eclipse depths are significantly larger than predicted for the best fit blackbody, suggesting the presence of an emission feature. On the nightside (phase $0.9$), the \Spitzer\ $4.5\,\mu$m eclipse depth is \emph{smaller} than predicted, suggesting an absorption feature. These differences indicate changes in thermal structure with longitude in the atmosphere.

@@

\subsection{Grid-Based Retrieval}
Since the phase-resolved spectra do not show spectrally resolved molecular features, we opted for a simple grid-based fit to the planet's atmospheric properties, similar to the grid search used in \cite{arcangeli18, mansfield18}. We generated a grid from one-dimensional forward models of the atmosphere over a broad range of metallicities, carbon-to-oxygen ratios (C/O), and stellar irradiation. The stellar spectrum is scaled in intensity over the grid to model the unknown heat redistribution for the planet; i.e., a lower dayside irradiation is equivalent to more efficient heat transport to the nightside.

@@

\subsubsection{Dayside Spectrum}
The main characteristics of the dayside emission spectrum are: (1) it is blackbody-like at WFC3 wavelengths, and (2) in the \Spitzer\ bands, the planet-to-star flux is significantly higher than predicted for the best fit blackbody, indicating an emission feature.  The best fit spectrum reproduces these data fairly well, with $\chi^2_\nu$ = 1.77. The largest contribution to the $\chi^2$ value is the $4.5\,\mu$m eclipse depth, which is larger than the best fit model prediction by $2.9\,\sigma$. When the $4.5\,\mu$m point is removed, the fit has $\chi^2_\nu = 1.17$.  The best fit model has a moderately enhanced metallicity ($23\times$ solar), carbon-to-oxygen equal to 0.76, poor heat redistribution, and a thermal inversion (temperature increasing with altitude).

@@

Figure\,\ref{fig:opacities} shows the opacity contributions of key absorbers for the best fit model.  In the optical (which we do not observe directly), there is strong absorption by TiO, VO, and FeH.  In the near-infrared, H$_2$O, H-, and hydrides/oxides all contribute to the opacity, leading to nearly constant opacity over the WFC3 wavelength range.  In cooler atmospheres, water is the dominant absorber over this bandpass \citep[e.g.][]{kreidberg14b, line16}, but in WASP-103b, H$_2$O is partially dissociated in the photosphere, leading to a drop in abundance by a factor of $\sim10$ (see Figure\,\ref{fig:summary}). Water also has intrinsically weaker features at high temperature \citep{tinetti12}. Water is also an efficient coolant, so lower water abundance leads to a more isothermal photosphere, which further weakens the contrast in and out of the water band. On top of this, there is significant H- opacity from single H atoms bound with free electrons, which fills in the opacity at wavelengths shorter than $1.5\,\mu$m.  Taken together, all these factors conspire to produce a nearly featureless spectrum from $1.1 - 1.7\,\mu$m. Finally, in the infrared the dominant absorber is CO, which produces the emission feature at \Spitzer\ wavelengths.

@@

We selected spectra from WASP-103b at three orbital phases: dayside ($\phi = 0.5$), quadrature ($\phi = 0.25$), and nightside ($\phi = 0.1$), and compared them to sources with comparable effective temperature. Figure\,\ref{fig:planetstarcomparison} shows the flux-calibrated spectra (assuming a distance of 10 pc).  The directly imaged spectra are taken from \cite{wahhaj11, aller13, bonnefoy14}. They are calibrated in absolute flux using published H-band photometry \citep{wahhaj11, bonnefoy09, aller13} and distances \citep{gaia16}, a flux-calibrated spectrum of Vega \citep{1985A&A...151..399M, 1985IAUS..111..225H}, and the corresponding filter passbands.  The brown dwarf spectra \textbf{Jackie: describe catalog of brown dwarf spectra and flux calibration}.

@@

We compared the spectra over the wavelength range $1.1 - 1.7\mu$m. The dominant opacity source over this range is water, which has a forest of absorption lines near 1.4\,$\mu$m. Spectra for the brown dwarfs and imaged companions have noticeable features in the water band, whereas WASP-103b does not. To quantitatively compare the water feature amplitude for different objects, we define an amplitude $A = (F_{1,2} - F_{3,4})/F_{1,2}$, where $F_{1,2}$ is the weighted mean flux in a wavelength bin $\lambda_1 - \lambda_2$. We calculated the water feature amplitude for two choices of wavelength bins. For the first, $A_1$, we considered data in and out of the water band, with $\lambda_{1,2,3,4} = 1.15, 1.3, 1.35, 1.5\,\mu$m. The ground-based direct imaging data doesn't span this entire wavelength range, so we also define an amplitude $A_2$ with $\lambda_{1,2,3,4} = 1.2, 1.35, 1.5, 1.65\,\mu$m. The estimated amplitudes and uncertainties are listed in Table\,\ref{table:sources}.

@@

	\item{We ran several 3D GCMs to compare to the data, including a nominal model with a cloud-free, solar composition, a metal-enriched model ([Fe/H] = 0.5), and two models with Lorentz drag. The GCMs with Lorentz drag have slower wind speeds and provide the best match to the data small hotspot offsets that are observed, but they underpredict the planet's nightside flux.}

>>>>

\author{Gregory W. Henry}
\affiliation{Center of Excellence in Information Systems, Tennessee State University, Nashville, TN 37209, USA}

@@

\begin{abstract}
	We present thermal phase curve measurements for the hot Jupiter WASP-103b observed with \emph{Hubble}/WFC3 and \emph{Spitzer}/IRAC. The dayside planet-to-star flux is $0.151\pm0.015\%$, $0.446\pm0.38\%$, and $0.569\pm0.014\%$ in bandpasses centered at $1.4$, $3.6$, and $4.5\mu$m, respectively.  The phase curves have large amplitudes and negligible hotspot offsets, indicative of poor heat redistribution to the nightside. We fit the phase variation with a range of climate maps and find they all provide reasonable fits to the data, but have large degeneracies in temperature (up to 1000 K for a given latitude/longitude). The phase-resolved spectra are consistent with blackbodies in the WFC3 bandpass, with effective temperatures ranging from 2000 K on the nightside to 3000 K on the dayside. However, the dayside spectrum has a strong feature in the \Spitzer\ bands, which we attribute to CO emission and a thermal inversion.  The emission feature is not present on the nightside, suggesting changing thermal structure with longitude. We retrieved the atmospheric composition with a 1D thermochemical equilibrium model and found the composition is moderately metal-enriched ($\mathrm{[M/H]} =  23^{+29}_{-13}\times$ solar), and the carbon-to-oxygen ratio is below 0.9 at $3\,\sigma$ confidence. In contrast to other hot Jupiters, we do not detect significant water absorption, which we attribute to partial H$_2$O dissociation and additional opacity from H- and TiO/VO.  We compare the phase curves to 3D general circulation models and find that atmospheric drag is required to explain the small hotspot offsets, but that these models overpredict the phase curve amplitude.  We also compare the WASP-103b spectra to brown dwarfs and young directly imaged companions and find they have significantly larger water features, indicating that surface gravity and irradiation environment play an important role in shaping the spectra of hot Jupiters. These results highlight the 3D structure of exoplanet atmospheres and illustrate the importance of phase curve observations for understanding their complex chemistry and physics.
\end{abstract}

@@

Exoplanets are so distant that they are not spatially resolved, so the only way to reveal inhomogeneity in their atmospheres is to measure a phase curve. Phase curve observations consist of continuous monitoring of the planet-to-star flux ratio over a complete orbital revolution of the planet, which exposes different longitudes at each orbital phase.  The first phase curve was observed with \Spitzer\ for the hot Jupiter HD 189733b by \citep{knutson07}, followed by additional \Spitzer\ observations for about a dozen more systems \citep[cataloged in][]{parmentier17}.  The observations revealed large day-night temperature contrasts (in excess of 300 K), and eastward shifted peak brightness due to heat circulation, as predicted by 3D models \citep{showman09}.  These infrared measurements were complemented by optical phase curves from \Kepler\ that show evidence for reflected light from patchy and variable dayside clouds with a range of compositions \citep{demory13, hu15, armstrong16, parmentier16}. A \emph{spectroscopic} phase curve was observed for WASP-43b with \emph{Hubble}/Wide Field Camera 3 (\HST/WFC3) in the near-infrared, which provided the first phase-resolved measurements of an exoplanet's water abundance and thermal structure \citep{stevenson14, stevenson17}.

@@

WASP-103b is an archetype of the class of ultra-hot Jupiters, with orbital periods of about one day and dayside temperatures typically $>2000\,\mathrm{K}$ FIXME \citep[e.g. WASP-12b, WASP-18b, WASP-19b, WASP-33b, WASP-43b, WASP-121b][]{}. Observations of the thermal emission spectra of these objects have been puzzling. In the near-infrared, where water is the dominant absorber, some spectra show water absorption features, some show emission features, and some are consistent with blackbody models \citep{madhusudhan11, crossfield12, stevenson14b, haynes15, evans16, beatty17a, beatty17b, sheppard17, arcangeli18, mansfield18}.  A variety of explanations have been proposed for these results, including low metallicity or high carbon-to-oxygen compositions, dayside clouds, and isothermal or inverted temperature profiles caused by TiO/VO absorption in the upper atmosphere. Recently, \cite{arcangeli18} showed that water dissociation on the hot dayside plays an important role in the atmospheres of these ultra-hot planets and may be responsible for some of the blackbody-like near-IR spectra. In this work, we put these results in context by investigating the global thermal structure and composition of the ultra-hot Jupiter WASP-103b.

The structure of the paper is the following: in \S\,\ref{sec:observations} we describe the observations and data reduction. \S\,\ref{sec:fits} details the models fit to the phase curves. In \S\,\ref{sec:results} we discuss results, including the phase curve amplitudes and hotspot offsets, the phase-resolved spectra, and estimates of the planet's climate. In \S\,\ref{sec:gcm} and \ref{sec:comparison}, we compare the observations to general circulation model (GCM) predictions and spectra from similar temperature stars and directly imaged companions. \S\,\ref{sec:summary} concludes.

@@

\subsection{\Spitzer}
We also obtained \Spitzer/IRAC observations with 3.6 and 4.5 $\mu$m photometric filters (referred to as Channel 1 and Channel 2, respectively). The observations had the following setup. Each phase curve observation consisted of 30 hours of time series photometry, beginning three hours prior to one secondary eclipse and ending three hours after a second eclipse.  We used 12 s exposures to maximize the duty cycle without saturating the detector. The data volume is relatively low for this exposure time, so we read out the full array. To minimize the intrapixel effect (variations in flux caused by imprecise pointing), we did not dither and also used PCRS peak-up\footnote{\url{http://irsa.ipac.caltech.edu/data/SPITZER/docs/irac/pcrs\_obs.shtml}} to improve the pointing accuracy. We began each observation with a 30-minute position settling period, followed by three Astronomical Observation Requests (AORs) of equal duration. At the beginning of each AOR, the telescope was repointed to position the target in the ``sweet spot" of the detector.

@@

The photometric analyses are summarized for each observing season in Table\,\ref{tab:photometry}.  The standard deviation of WASP-103's brightness in each season is given in column~4.  The mean of the three standard deviations is 0.0058~mag, which is very comparable to the mean standard deviation of the six comparison stars (0.0055~mag).  To maximize the possibility of detecting WASP-103b's rotation, we normalized the photometry such that each observing season has the same mean, thereby removing any long-term variability in WASP-103 and/or the comparison stars (Figure\,\ref{fig:photometry}, top panel).  We performed a periodogram analysis of the normalized data set based on least-squares fitting of sine curves.  The resulting frequency spectrum and the phase curve computed with the best period are shown in the middle and lower panels of Figure\,\ref{fig:photometry} respectively. The best-fit period is 6.814 days, which agrees closely with the estimated stellar rotation period of 6.855 days of \citep{gillon14}. The peak-to-peak variability amplitude is 0.005 mag.  Based on the formalism in \cite{zellem17}, we calculate that this variability will bias the measured eclipse depth by $\lesssim10$\,ppm from epoch to epoch, which is well below the photon-limited precision of our measurements.

@@

\section{Light Curve Fits}
\label{sec:fits}
We fit a two-component model to the light curves. One component models the astrophysical signal (the planet's thermal phase variation and transit), and the other component models the systematic noise introduced by time-dependent changes in instrument performance. For each light curve, we fit the physical and systematic components simultaneously, such that the total observed flux as a function of time is given by $F(t) = F_\mathrm{physical}(t) \times F_\mathrm{sys}(t)$. For the \HST\ data, where we observed two phase curves and two additional eclipses, we constrain the physical parameters to be the same for all visits, but allow some of the systematics parameters to vary (for more details see \S\,\ref{sec:hst_sys}). We fit the WFC3 band-integrated ``white" light curve, as well as spectroscopic light curves created from 10 wavelength bins uniformly spaced at $0.05\,\mu$m intervals between $1.15$ and $1.65\,\mu$m.

@@

Some segments of the data exhibit stronger systematics than others, so we exclude these data in our final analysis. We drop the first orbit from every visit and the first exposure from every orbit \citep[following common practice; see e.g.][]{kreidberg14a}.  We also discard exposures from the last half of orbit 15 from the phase curve observations, which were taken in staring mode to enable a gyro bias update. Since we observed two phase curves, we have complete orbital phase coverage of the planet despite discarding some data.

@@

In addition to calculating the fit rms compared to the photon noise, we also tested for the presence of red noise based on whether the rms decreases as expected when the light curve in binned in time.  If the noise is white (uncorrelated in time), the residuals are expected to decrease by a factor of $\sqrt{N}$, where $N$ is the number of points in a bin. Figure\,\ref{fig:rms} shows the binned residuals compared to expectations for white noise. The \HST/WFC3 and \Spitzer\ Channel 2 light curves agree well with expectations, whereas \Spitzer\ Channel 1 shows higher noise than expected as bin size increases. This test confirms the presence of time-correlated noise in the Channel 1 light curve that can be seen by eye in the residuals in Figure\,\ref{fig:phasecurves}. Both \Spitzer\ channels use the same detector, but Channel 1 data are more susceptible to time-correlated noise because the the point spread function is narrower at shorter wavelengths, making intrapixel sensitivity variations more pronounced.

@@

\section{Results}
\label{sec:results}
The fitted light curves are shown in Figure\,\ref{fig:phasecurves}. This figure shows results from the spherical harmonics model for the thermal phase variation and has instrument systematics removed.  Broadly speaking, the phase curves show large dayside planet-to-star flux values, ranging from $0.151\pm0.015\%$, $0.446\pm0.38\%$, and $0.569\pm0.014\%$ in the WFC3 white light curve, and \Spitzer\ $3.6$, and $4.5\mu$m bandpasses, respectively.  The planet flux changes significantly with orbital phase in all three of the data sets, suggesting a strong gradient from dayside to nightside temperature, and peak brightness occurs near phase 0.5. In this section, we quantitatively characterize the phase curve shape, split the data into phase resolved spectra, evaluate different temperature maps, and compare with previous observations of the dayside thermal emission spectrum.

@@

\begin{figure*}
\includegraphics[width = 1.0\textwidth]{Figures/hst_model_comparison.pdf}
\caption{\textbf{Left:} Fits to the broadband WFC3 phase curve compared to a GCM. The colored lines correspond to different temperature maps fit to the data, and the dashed gray line is from the $\tau_\mathrm{drag3}$ GCM. We also show the planet-to-star flux corresponding to each map (points), which is model-dependent due to slight degeneracies with the instrument systematic model.  \textbf{Right:} Temperature maps from the best fit models and the GCM at a pressure of 0.01 bar.}
\label{fig:model_comparison}
\end{figure*}

@@

\begin{figure}
\includegraphics[width = 0.5\textwidth]{Figures/dayside_spectrum.pdf}
\caption{Dayside planet-to-star flux (points) compared to the best fit 1-D model (blue line) with $1\,\sigma$ uncertainty shaded in orange. We also show the best fit blackbody model for the planet (fit to the WFC3 data only).}
\label{fig:dayside}
\end{figure}

\subsection{Climate}
We fit three different models to characterize the planet's climate: a two-temperature map, the physically-motivated kinematic model of \cite{zhang17}, and a spherical harmonic map. We also fit the thermal phase variation with a sinusoid, which can be inverted to map the climate \citep{cowan08}.  All of the models provide reasonable fits to the data, with $\chi^2_\nu$ near unity, but they yield significantly different temperature maps. Table\,\ref{table:model_comparison} lists the minimum and maximum temperatures for the best fit models to the WFC3 broadband and two Spitzer phase curves. We also list the  information criterion (BIC) and Aikike information criterion (AIC) values for the fits \citep[a $\Delta$BIC value greater than 10 constitutes strong evidence against a given model;][]{kass95}.

@@

We compared the planet's minimum and maximum temperature for the three climate maps by computing the temperatures over a $100\times100$ grid in latitude and longitude. The kinematic model has the hottest dayside temperature, and the two-temperature model has the smallest. The differences in peak temperature for the models we consider ranges from $630\,\mathrm{K}$ for \Spitzer\ Channel 1 to $1070\,\mathrm{K}$ for the broadband WFC3 light curve. The minimum nightside temperature is also model-dependent: for the WFC3 data, the two-temperature model predicts a nightside temperature of zero Kelvin, whereas the best fit kinematic model has a nightside temperature of $1980\,\mathrm{K}$.  These differences arise because the kinematic model allows a steep temperature gradient on the dayside, so the substellar point is much hotter than the terminator, whereas the two temperature map imposes a constant dayside temperature.  The spherical harmonics model has an intermediate temperature gradient and fits the data the best. However, this model may not be physically realistic: on the nightside, it produces higher temperatures at the poles than at the equator, contrary to predictions from GCMs (which we discuss in \S\,\ref{sec:gcm}).

@@

\subsection{Blackbody Fits}
A blackbody is the simplest model for the planet's thermal emission and provides a useful first evaluation of the atmospheric properties. The best-fit blackbodies are shown in Figures \ref{fig:spectra} and \ref{fig:dayside}. This model performs well for some orbital phases, with $\chi^2_\nu$ ranging from 0.9 to 1.1 for phases $\phi = 0.1, 0.7$ and $0.8$. At other phases the blackbody model is a poorer fit, particularly to the \Spitzer\ data. For phases $0.2 - 0.6$, the \Spitzer\ eclipse depths are significantly larger than predicted for the best fit blackbody, suggesting the presence of an emission feature (due to CO, as we discuss in \S\,\ref{sec:retrieval}). On the nightside (phase $0.9$), the \Spitzer\ $4.5\,\mu$m eclipse depth is \emph{smaller} than predicted, suggesting an absorption feature. These differences indicate changes in thermal structure with longitude in the atmosphere.

@@

\subsection{Grid-Based Retrieval}
\label{sec:retrieval}
Since the phase-resolved spectra do not show spectrally resolved molecular features, we opted for a simple grid-based fit to the planet's atmospheric properties, similar to the grid search used in \cite{arcangeli18, mansfield18}. We generated a grid from one-dimensional forward models of the atmosphere over a broad range of metallicities, carbon-to-oxygen ratios (C/O), and stellar irradiation. The stellar spectrum is scaled in intensity over the grid to model the unknown heat redistribution for the planet; i.e., a lower dayside irradiation is equivalent to more efficient heat transport to the nightside.

@@

\subsubsection{Dayside Spectrum}
The main characteristics of the dayside emission spectrum are: (1) it is blackbody-like at WFC3 wavelengths, and (2) in the \Spitzer\ bands, the planet-to-star flux is significantly higher than predicted for the best fit blackbody, indicating an emission feature.  The best-fit spectrum reproduces these data fairly well, with $\chi^2_\nu$ = 1.77. The largest contribution to the $\chi^2$ value is the $4.5\,\mu$m eclipse depth, which is larger than the best fit model prediction by $2.9\,\sigma$. When the $4.5\,\mu$m point is removed, the fit has $\chi^2_\nu = 1.17$.  The best fit model has a moderately enhanced metallicity ($23\times$ solar), carbon-to-oxygen equal to 0.76, poor heat redistribution, and a thermal inversion (temperature increasing with altitude).

@@

Figure\,\ref{fig:opacities} shows the opacity contributions of key absorbers for the best fit model.  In the optical (which we do not observe directly), there is strong absorption by TiO, VO, and FeH.  In the near-infrared, H$_2$O, H-, and hydrides/oxides all contribute to the opacity, leading to nearly constant opacity over the WFC3 wavelength range.  In cooler atmospheres, water is the dominant absorber over this bandpass \citep[e.g.][]{kreidberg14b, line16}, but in WASP-103b, H$_2$O is partially dissociated in the photosphere, leading to a drop in abundance by a factor of $\sim10$ (see Figure\,\ref{fig:summary}). Water also has intrinsically weaker features at high temperature \citep{tinetti12}. Water is also an efficient coolant, so lower water abundance leads to a more isothermal photosphere, which further weakens the contrast in and out of the water band. On top of this, there is significant H- opacity from single H atoms bound with free electrons, which fills in the opacity at wavelengths shorter than $1.5\,\mu$m.  Taken together, all these factors add up to produce a nearly featureless spectrum from $1.1 - 1.7\,\mu$m. Finally, in the infrared the dominant absorber is CO, which produces the emission feature at \Spitzer\ wavelengths.

@@

We selected spectra from WASP-103b at three orbital phases: dayside ($\phi = 0.5$), quadrature ($\phi = 0.25$), and nightside ($\phi = 0.1$), and compared them to sources with comparable effective temperature. Figure\,\ref{fig:planetstarcomparison} shows the flux-calibrated spectra (assuming a distance of 10 pc).  The directly imaged spectra are for the sources CD-35 2722, USco 1610-1913B, and TWA 22A and are taken from \cite{wahhaj11, aller13, bonnefoy14}. They are calibrated in absolute flux using published H-band photometry \citep{wahhaj11, aller13, bonnefoy09} and distances \citep{gaia16, teixeira09}, a flux-calibrated spectrum of Vega \citep{1985A&A...151..399M, 1985IAUS..111..225H}, and the corresponding filter passbands.  The brown dwarf spectra \textbf{Jackie: describe catalog of brown dwarf spectra and flux calibration}.

@@

We compared the spectra over the wavelength range $1.1 - 1.7\mu$m. The dominant spectral features over this range are expected to come from water, which has a forest of absorption lines near 1.4\,$\mu$m. Spectra for the brown dwarfs and imaged companions have noticeable features in the water band, whereas WASP-103b does not. To quantitatively compare the water feature amplitude for different objects, we define an amplitude $A = (F_{1,2} - F_{3,4})/F_{1,2}$, where $F_{1,2}$ is the weighted mean flux in a wavelength bin $\lambda_1 - \lambda_2$. We calculated the water feature amplitude for two choices of wavelength bins. For the first, $A_1$, we considered data in and out of the water band, with $\lambda_{1,2,3,4} = 1.15, 1.3, 1.35, 1.5\,\mu$m. The ground-based direct imaging data doesn't span this entire wavelength range, so we also define an amplitude $A_2$ with $\lambda_{1,2,3,4} = 1.2, 1.35, 1.5, 1.65\,\mu$m. The estimated amplitudes and uncertainties are listed in Table\,\ref{table:sources}.

@@

	\item{We ran several 3D GCMs to compare to the data, including a nominal model with a cloud-free, solar composition, a metal-enriched model ([Fe/H] = 0.5), and two models with Lorentz drag. The GCMs with Lorentz drag have slower wind speeds and provide the best match to the small hotspot offsets that are observed, but they underpredict the planet's nightside flux.}
